Mental Health Factors and Covid

### 2025-04-20 products/manuscript/Manuscript.qmd
Part 5 manuscript updates

Data was subsetted to years 2019-2022, to cover the brunt of pandemic years. Despite low prevelance of COVID-19 cases in 2019 worldwide, the appearance of COVID-19 in the news (and consequential potential impact on mental health factors) led us to include this data. The final dataset contains 151406 observations.

@@

This data was obtained from IPUMS, used with permission.

@@

The following code details the data cleaning process. Labels are removed from the data to make it easier to work with to create models later in the process. Variables needed are selected, then a series of binary varibales are created. Additional details are available in the processing folder.

## Statistical analysis
_Explain anything related to your statistical analyses._

We will begin with exploratory tables to explore proportions of NA answers, and generate early estimates.

Our first figure with be a discriptive table stratified by COVID status, with estimates and 95% CIs.

Next, we will construct simple models before moving onto adjusted models.

@@

The first table below details the proportion of NAs for each mental health variable. We can see this is a little bit high, which may affect analysis later on. Histograms of each variable are available in the eda folder.

The second table shows proportions calculated using complex survey design variables.

@tbl-summarytable shows a summary of the data.

>>>>

@@

National Health Information Survey data was obtained from IPUMS, used with permission. Data was subsetted to years 2019-2022, to cover the brunt of pandemic years. Despite low prevelance of COVID-19 cases in 2019 worldwide, the appearance of COVID-19 in the news (and consequential potential impact on mental health factors) led us to include this data. The final dataset contains 151406 observations.

@@

## Statistical analysis

@@

```{r}
#| label: fig-schematic
#| fig-cap: "Summary statistics table"
#| echo: FALSE
knitr::include_graphics(here("results","figures", "table1_imputed.png"))
```
